%% CV for JBT Marel - Controls Cybersecurity Engineer
%% Compiled with: lualatex

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Jacob El-Omar - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

\name{Jacob}{El-Omar}
\address{Aalborg, Denmark}{}{}
\phone[mobile]{+45 53 35 27 82}
\email{elomarjc@gmail.com}
\extrainfo{\href{https://linkedin.com/in/jacob-el-omar}{LinkedIn} \textbullet{} \href{https://github.com/elomarjc}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE
% ============================================================

\vspace{6pt}
\small{MSc Graduate in Electronic Systems from Aalborg University specializing in control engineering, embedded software, and real-time systems. Experienced in designing control loops (LQR, PID), state estimation (Kalman filtering), embedded C/C++ microcontrollers, and Python data pipelines. Proficient in leveraging agentic AI workflows with Claude Code for rapid test scripting, technical documentation, and compliance mapping. Motivated to contribute to secure industrial automation, Cyber Resilience Act (CRA) compliance, and PLC/HMI controls platform development at JBT Marel in Støvring.}

% ============================================================
%     TECHNICAL SKILLS
% ============================================================

\section{Technical Skills}
\vspace{1pt}
\begin{itemize}

\item \textbf{Control Systems \& Automation}: Control loop design (LQR, PID, robust control), system identification, state estimation (Kalman filters), MATLAB \& Simulink, industrial control concepts.

\item \textbf{Embedded \& PLC Programming}: C/C++, Cypress PSoC microcontrollers, I2C/SPI/UART protocols, EtherNet/IP, OPC-UA concepts, hardware-software co-design.

\item \textbf{Software Development \& Analysis}: Python (NumPy, SciPy, Pandas), C\#, SQL databases, Git, automated testing pipelines, technical compliance documentation.

\item \textbf{AI Tools \& Methodologies}: Agentic AI workflows with Claude Code for code generation, test automation, and documentation. Problem-Based Learning (PBL) team collaboration.

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

\item{\cventry{Jan 2026--Present}{IT \& Web Developer (Volunteer)}{Dawah Danmark}{Aalborg, Denmark}{}{\vspace{1pt}
\begin{itemize}
    \item Developed and maintained organizational backend infrastructure and database architectures.
    \item Optimized system performance, data security, and platform stability.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{Sep 2024--Jun 2025}{AI/ML Engineer (Internship)}{Ai Health Highway}{Remote}{}{\vspace{1pt}
\begin{itemize}
    \item Engineered and validated signal processing algorithms in Python for diagnostic equipment.
    \item Executed real-time filtering, data validation, and technical documentation in compliance with diagnostic standards.
\end{itemize}}}

\vspace{3pt}

\item{\cventry{Jun 2023--Aug 2024}{Logistics Specialist}{Lyn Express}{Aalborg, Denmark}{}{\vspace{1pt}
\begin{itemize}
    \item Managed inventory workflows, sorting logistics, and time-critical operations under pressure.
    \item Built automated Excel macros for administrative tracking and reporting efficiency.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{Sep 2023--Jun 2025}{MSc in Engineering (Electronic Systems)}{Aalborg University}{Aalborg, Denmark}{}{\vspace{1pt}
Thesis: ``Adaptive Noise Cancellation For Electronic Stethoscopes.'' Focus on real-time signal processing, control theory, and Python/MATLAB algorithm pipelines.
}}

\vspace{3pt}

\item{\cventry{Sep 2020--Aug 2023}{BSc in Engineering (Electronics and IT)}{Aalborg University}{Aalborg, Denmark}{}{\vspace{1pt}
Specialization in control systems, robotics, and embedded C programming. Projects included model gantry crane control systems and Cypress PSoC fall-detection systems.
}}

\end{itemize}

% ============================================================
%     SELECTED PROJECTS
% ============================================================

\section{Udvalgte Projekter}
\vspace{1pt}
\begin{itemize}

\item{\textbf{Autonomous Gantry Crane Control System (Bachelorprojekt, Universitetsprojekt)}: Modeled physical crane dynamics, designed LQR/PID control loops in MATLAB/Simulink, and implemented real-time anti-sway control logic.}

\item{\textbf{Embedded Fall-Detection System (Universitetsprojekt)}: Programmed a real-time fall-detection algorithm on a Cypress PSoC microcontroller in C, establishing sensor I2C communication and interrupt handlers.}

\item{\textbf{Grow a Fish (Fritidsprojekt)}: Developed a full-stack mobile application using Flutter and Dart with a Supabase PostgreSQL backend, REST APIs, and database sync.}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item English (Fluent), Danish (Native).
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item Available upon request.
\end{itemize}

\end{document}
