%% Example CV - Jacob El-Omar
%% Comprehensive overview of all competencies, experience, and achievements.
%% Use as a master reference when tailoring role-specific CVs.
%%
%% Compile with: lualatex main_example.tex
%% (pdflatex often fails on modern MiKTeX with fontawesome5 font-expansion errors.)

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{banking}
\moderncvcolor{blue}

% Force both first and last name AND section headings to render in moderncv
% blue (color1). Default banking on lualatex+MiKTeX leaves these black, which
% looks inconsistent with the rest of the blue accent scheme.
\renewcommand*{\firstnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\lastnamestyle}[1]{{\fontsize{34}{36}\bfseries\upshape\color{color1}#1}}
\renewcommand*{\sectionstyle}[1]{{\sectionfont\color{color1}#1}}

\usepackage[utf8]{inputenc}
\usepackage{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
    pdftitle={Jacob El-Omar - CV},
    pdfpagemode=FullScreen,
}
\usepackage[scale=0.80]{geometry}
\usepackage{import}

% personal data
\name{Jacob}{El-Omar}
\address{Aalborg, Denmark}{}{}
\phone[mobile]{+45 53 35 27 82}
\email{elomarjc@gmail.com}
\extrainfo{\href{https://linkedin.com/in/jacob-el-omar}{LinkedIn} \textbullet{} \href{https://github.com/elomarjc}{GitHub}}

\begin{document}

\makecvtitle

% ============================================================
%     PROFILE STATEMENT
% ============================================================

\vspace{6pt}
\small{Recent MSc graduate in Electronic Systems from Aalborg University (graduated June 2025), specializing in software development, embedded systems, and signal processing. Following my graduation, the gap in my employment history is due to a rewarding parental leave during which I cared for my two young children. I am now fully prepared, highly motivated, and excited to launch my professional career and contribute to your team from day one.}

% ============================================================
%     CORE COMPETENCIES
% ============================================================

\section{Core Competencies}
\vspace{1pt}
\begin{itemize}

\item \textbf{Programming Languages \& Frameworks}: C\#, .NET Core, Python, Flutter, Dart, C, C++, JavaScript, TypeScript, Node.js, SQL, VHDL.

\item \textbf{Embedded Systems \& IoT}: Microcontrollers (Cypress PSoC), Sensor Integration (I2C, IMU), Altium Designer, Onshape, CNC, FPGA.

\item \textbf{Signal Processing \& Control Systems}: Adaptive Filtering (LMS, NLMS, RLS, FastICA), LQR, Kalman Filtering, Robotics (MiR200).

\item \textbf{Web Development}: WordPress, Web Development, User Experience, Plugins.

\item \textbf{Methodologies \& Tools}: git, GitHub Actions (CI/CD), Scrum, Problem-Based Learning (PBL).

\end{itemize}

% ============================================================
%     PROFESSIONAL EXPERIENCE
% ============================================================

\section{Professional Experience}
\vspace{3pt}
\begin{itemize}

% --- Most Recent Role ---
\item{\cventry{Jan 2026--Present}{IT \& Web Developer (Volunteer)}{Dawah Danmark}{Aalborg, Denmark}{}{\vspace{1pt}
\begin{itemize}
    \item Modernized and maintained the organizational WordPress platform to ensure consistent site reliability and performance.
    \item Optimized website architecture and integrated plugins to elevate user experience and operational efficiency.
\end{itemize}}}

\vspace{3pt}

% --- Previous Role ---
\item{\cventry{Sep 2024--Jun 2025}{AI/ML Engineer (Internship)}{Ai Health Highway}{Remote}{}{\vspace{1pt}
\begin{itemize}
    \item Engineered and deployed signal enhancement solutions for smart stethoscopes (AiSteth) utilizing adaptive filtering algorithms (LMS, NLMS, RLS) and FastICA for high-noise medical environments.
    \item Partnered with international research teams to refine diagnostic algorithms for cardiovascular and pulmonary disease screening.
    \item Verified signal integrity and model performance in compliance with stringent medical-grade diagnostic standards.
    \item Produced rigorous technical documentation and research reports to support data-driven stakeholder decision-making.
\end{itemize}}}

\vspace{3pt}

% --- Logistics Role ---
\item{\cventry{Jun 2023--Aug 2024}{Lager- og Logistikmedarbejder}{Lyn Express}{Aalborg, Denmark}{}{\vspace{1pt}
\begin{itemize}
    \item Streamlined inventory and logistics operations, managing the receiving, sorting, and numbering of shipments.
    \item Maintained operational excellence and strict adherence to protocols to optimize delivery workflows in a high-pressure environment.
\end{itemize}}}

\vspace{3pt}

% --- Service Assistant ---
\item{\cventry{Oct 2017--Jan 2018}{Service Assistant}{Fakta A/S}{Aalborg, Denmark}{}{\vspace{1pt}
\begin{itemize}
    \item Delivered professional customer service and ensured positive service experiences in a fast-paced environment.
    \item Managed store structure, cleanliness, and operational tasks, demonstrating reliability and team collaboration.
\end{itemize}}}

\end{itemize}

% ============================================================
%     EDUCATION
% ============================================================

\section{Education}
\vspace{1pt}
\begin{itemize}

\item{\cventry{Sep 2023--Jun 2025}{MSc in Engineering (Electronic Systems)}{Aalborg University}{Aalborg, Denmark}{}{\vspace{1pt}
Thesis: ``Adaptive Noise Cancellation For Electronic Stethoscopes.'' Focus on stochastic systems, machine learning, signal processing, and real-time embedded platforms.
}}

\vspace{3pt}

\item{\cventry{Sep 2020--Aug 2023}{BSc in Engineering (Electronic Engineering and IT)}{Aalborg University}{Aalborg, Denmark}{}{\vspace{1pt}
Specialization in Control Engineering. Project: Autonomous Control System designed for a model gantry crane, and developed predictive collision-avoidance systems for MiR200 robotic platforms.
}}

\end{itemize}

% ============================================================
%     LANGUAGES
% ============================================================

\section{Languages}
\vspace{1pt}
\begin{itemize}
\item Danish (native), English (fluent).
\end{itemize}

% ============================================================
%     HONORS AND AWARDS
% ============================================================

\section{Honors and Awards}
\vspace{1pt}
\begin{itemize}
\item{\textbf{1st Place, RoboCup Tournament} -- Aalborg University (2020). Won the robotics tournament with optimized control algorithms.}
\end{itemize}

% ============================================================
%     REFERENCES
% ============================================================

\section{References}
\vspace{1pt}
\begin{itemize}
\item{Available upon request.}
\end{itemize}

\end{document}
